---
title: "Bayesian Mixed-Effects model of Pulse Pressure Variation by Tidal Volume and Respiratory Rate"
output:
  bookdown::pdf_document2:
    extra_dependencies: ["underscore", "float"]
    toc: no
    dev: cairo_pdf
    keep_tex: no
    latex_engine: xelatex
# toc-title: "Contents"
fontsize: 11pt
linkcolor: NavyBlue
monofont: FreeMono
monofontoptions: 'Scale=0.8'
mainfontoptions: 'Linestretch=4'
---

This document presents code for fitting, analysing and visualising the Bayesian mixed-effects model presented in the paper.
It includes a presentation of model priors, with arguments for why they are considered weakly informative. 

```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(echo = TRUE,
                      fig.align= 'center')
knitr::opts_knit$set(root.dir = here::here())
```

# Setup

```{r packages, message=FALSE}
library(tidyverse)
library(patchwork) # For combining plots

library(brms)      # For fitting Stan models
library(tidybayes) # For working with fitted Stan models 
options(mc.cores = parallel::detectCores())

source("plot_settings.R") # Plot theme and utility functions
theme_set(theme_paper())
```

# Load data

Data is shared in the `data/` folder in the code repository:

<https://github.com/JohannesNE/supplementary-PPV-ventilation-paper>

A codebook is available in the same folder.

```{r, message=FALSE}
PPV_df <- read_csv("data/vent_setting_study-ppv.csv") |> 
  mutate(
    # Create factors for ventilator settings
    id_f = factor(id),
    vent_rel_vt_f = factor(vent_rel_vt, levels = c(10, 8, 6, 4)),
    vent_RR_f = factor(vent_RR, levels = c(10, 17, 24, 31)),
    vent_setting = interaction(vent_rel_vt, vent_RR, drop = TRUE) |> 
      forcats::fct_relevel("10.10", "8.10", "6.10", "4.10",
                           "8.17", "6.17",
                           "8.24", "6.24",
                           "8.31", "6.31")
  ) |> 
  # Remove the 13 / 520 rows without a PPV value. PPV is missing either because the
  # ventilator setting was not applied or because PPV estimation was infeasible 
  # because of frequent extra-systoles (≥3 in one window).
  drop_na(PPV_gam) 

# Labels for vent settings
vent_setting_levels <- c(
  "10.10" = "VT=10, RR=10",
  "8.10" = "VT=8, RR=10",
  "6.10" = "VT=6, RR=10",
  "4.10" = "VT=4, RR=10",
  "8.17" = "VT=8, RR=17",
  "6.17" = "VT=6, RR=17",
  "8.24" = "VT=8, RR=24",
  "6.24" = "VT=6, RR=24",
  "8.31" = "VT=8, RR=31",
  "6.31" = "VT=6, RR=31"
)

vt_levels <- c(
  "10" = "VT=10",
  "8" = "VT=8",
  "6" = "VT=6",
  "4" = "VT=4"
)

rr_levels <- c(
  "10" = "RR=10",
  "17" = "RR=17",
  "24" = "RR=24",
  "31" = "RR=31"
)

# Pivot PPV data frame to long format with one column for PPV
# and one column indicating the method (Classic or GAM)
PPV_df_long <- PPV_df |> 
  pivot_longer(c(PPV_gam, PPV_classic),
               values_to = "PPV",
               names_to = "PPV_method",
               names_prefix = "PPV_") |> 
  mutate(PPV_vt = 10*PPV/vent_rel_vt,
         label = vent_setting_levels[as.character(vent_setting)] |> 
           factor(levels = vent_setting_levels),
         PPV_method = factor(PPV_method, levels = c("gam", "classic"))) 
```

# Model specification

The model (m1), fitted with brms, corresponds to the following model in mathematical notation:

\begin{align*}
&\text{\bfseries [Likelihood]} \\
PPV_i \sim &StudentT(\mu_i,\sigma_i, \text{df} = 4) \\
&\text{\bfseries [Linear model of } log(\mu)] \\
log(\mu_i) = &
\beta0_{\operatorname{PPVmethod}[i]} + 
\beta1_{\operatorname{ventVT}[i]\times\operatorname{PPVmethod}[i]} +
\beta2_{\operatorname{ventRR}[i]\times\operatorname{PPVmethod}[i]} +
\alpha_{subject[i]} \\
%
&\text{\bfseries [Addaptive prior for random effect of subject]} \\
\alpha_s \sim &Normal(0, \sigma_{\alpha}) \\
&\quad\text{, for subject s = 1,} \dots \text{,52} \\
%
&\text{\bfseries [Prior for SD of subjects]}\\
\sigma_\alpha \sim &truncNormal(0, 1.5, low = 0) \\
%
&\text{\bfseries [Prior for PPVmethod-specific intercept]} \\
\beta0_{m} \sim &Normal(2.3, 1) \\
&\quad\text{, for PPVmethod m = (gam, classic)} \\
%
&\text{\bfseries [Prior for } \beta s]\\
(\beta1_{t,m},\beta2_{r,m}) \sim &Normal(0, 2) \\
&\quad\text{, for ventVT t = (8,6,4); ventRR r = (17,24,31); PPVmethod m = (gam, classic)} \\
% Sigma model
&\text{\bfseries [Linear model of } log(\sigma)]\\
log(\sigma_i) = &
\gamma0_{\operatorname{PPVmethod}[i]} + 
\gamma1_{\operatorname{ventVT}[i]\times\operatorname{PPVmethod}[i]} +
\gamma2_{\operatorname{ventRR}[i]\times\operatorname{PPVmethod}[i]} \\
% Sigma prior
&\text{\bfseries [Prior for } \gamma s \text{]} \\
(\gamma0_{m},\gamma1_{t,m},\gamma2_{r,m}) \sim &Normal(0, 1.5) \\
&\quad\text{, for ventVT t = (8,6,4); ventRR r = (17,24,31); PPVmethod m = (gam, classic)}
\end{align*}

All independent variables are categorical. $PPVmethod$ is one of the categories “GAM” or “Classic”, $ventVT$ is one of the tidal volumes 10, 8, 6 or 4 ml kg^-1^ (10 ml kg^-1^ is the reference), $ventRR$ is one of the respiratory rates 10, 17, 24 or 31 min^-1^ (10 min^-1^ is the reference). The random term ($\alpha_s$) allows a subject specific intercept, reflecting that each subject presents with PPVs in different ranges. 

Model 2 (m2) is similar, but instead of separate effects of tidal volume ($ventVT$) and respiratory rate ($ventRR$), the two ventilator settings are combined to $ventSetting$, giving estimates of all 10 applied combinations of tidal volume and respiratory rate.

## Priors

First we present the model priors. Generally these are weakly informative and only exclude unreasonably large effects.
They simply serve as computational aids for fitting the model.

```{r message=FALSE, warning=FALSE}
# Population-level terms -------------------------------------
# Because of the log-link, these terms represent the log of the 
# multiplicative effect on the outcome scale.
priors_pterms <- c(
  # Prior for the default population level effects.
  # A normal distribution with SD = 2, means that any effect of ventilator settings
  # different than VT=10, RR=10 is probably (68% interval) between a 7x increase 
  # and a 7x decrease in PPV. 95% prior interval exp(c(-4, 4) ~ 1/50 to 50.
  set_prior("normal(0, 2)", class = "b"), 
  # Intercept (median PPV) is probably between 3 and 30 (i.e. exp(c(1.3, 3.3)) )
  # 95% prior interval ~ 1.4 to 73
  set_prior("normal(2.3, 1)", coef = "PPV_methodgam"),
  set_prior("normal(2.3, 1)", coef = "PPV_methodclassic")
)

# Variability terms -------------------------------------
# Between-subject variability (random effect) 
# and within-subject variability (residuals)
priors_ranef <- c(
  # Prior for sd of random effect (half-normal prior).
  # Since this effect is on the log scale, a sd of 1 would mean that 
  # 68 % of subjects are within 2.7x below and above the value predicted from
  # the fixed effects.
  set_prior("normal(0,1.5)", class = "sd"), 
  # Priors for the linear predictors of log(sigma): The residual variability. 
  # This gives 68% prior probability that sigma at VT=10,RR=10 is in the
  # range exp(c(-1.5, 1.5)) = 0.22 to 4.48.
  # The relative effect of VT and RR on sigma is assumed to be less than 4.5x (each).
  set_prior("normal(0,1.5)", dpar = "sigma") 
)

priors <- c(priors_pterms, 
            priors_ranef)
```

## Model sampling

The models are sampled using Stan, via the R interface `brms`. Four chains with 4000 post-warmup draws each were used.

```{r message=FALSE, warning=FALSE}
m1 <- 
  brm(bf(PPV ~
           0 + PPV_method + (vent_rel_vt_f + vent_RR_f):PPV_method +
           (1 | id_f), 
         sigma ~ 0 + PPV_method + (vent_rel_vt_f + vent_RR_f):PPV_method,
         # We fix nu (degrees of freedom in T distribution)
         nu = 4
  ),
  prior = priors,
  data = PPV_df_long,
  seed = 1,
  iter = 6000,
  warmup = 2000,
  family = student(link = "log"),
  file = "temp_model_fits/m1",
  file_refit = "on_change")

# Model with interaction between VT and RR
m2 <- 
  brm(bf(PPV ~
           0 + PPV_method + vent_setting:PPV_method +
           (1 | id_f), 
         sigma ~ 0 + vent_setting:PPV_method,
         nu = 4
  ),
  prior = priors,
  data = PPV_df_long,
  seed = 1,
  iter = 6000,
  warmup = 2000,
  family = student(link = "log"),
  file = "temp_model_fits/m2",
  file_refit = "on_change")
```

# Convergence

We consider that models have converged if `Rhat` for all parameters are < 1.01 (for details on the `Rhat` convergence measure, see [Vehtari et al, 2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%CB%86-for/10.1214/20-BA1221.full)). 

```{r}
rhat_m1 <- rhat(m1) |> na.omit() # when nu is fixed, Rhat for nu is NaN
rhat_m2 <- rhat(m2) |> na.omit()

stopifnot(max(rhat_m1) < 1.01)
stopifnot(max(rhat_m2) < 1.01)
```

m1: `max(rhat(m1))` = `r max(rhat_m1)`

m2: `max(rhat(m2))` = `r max(rhat_m2)`

# Posterior predictive plots

Below are plots showing the posterior prediction of PPV for all 10 ventilator settings 
(8.10.gam means VT=8 ml kg^-1^, RR=10 min^-1^ with GAM method). 
The Student t distribution of the response places a (very) small area of the predictive distribution in negative PPV values. 
Negative PPV values are not possible. 
We also fitted the models with a lower bound of 0 on the response distribution, eliminating negative predictions. 
That model gave essentially identical results, so we decided to use the non-bounded distribution, as it's location parameter ($\mu$) is equal to the expected value, allowing interpretation of model parameters as conditional effects on the expected value of PPV.

```{r}
bayesplot::ppc_dens_overlay_grouped(
  m1$data$PPV, 
  yrep = posterior_epred(m1, ndraws = 50),
  group = with(m1$data, interaction(vent_rel_vt_f, vent_RR_f, PPV_method))) +
  labs(title = "m1 - Posterior predictive plots (VT.RR.method)",
       x = "PPV") +
  scale_x_continuous(limits = c(-5, 25))
```

We only include the posterior predictive distributions for m1. The plots for m2 look practically identical.

# Pareto K diagnostic and comparison of m1 and m2

```{r}
loo(m1, m2)
```

All Pareto k are < 0.5 for both models, indicating that we do not have any overly influential data points. The higher elpd of model 1 indicates that this model is probably preferable (it is both simpler and performs better in cross-validation). In the paper we only consider model 1 as it is simpler to interpret. Here, we present both for completeness.

## Variation in data explained by the model

```{r}
bayes_R2(m1)
```

Model 1 explains ~83% of the variation in data.

```{r}
bayes_R2(m1, re_formula = NA)
```

If we exclude the random effects (between individual variation), we can see that the fixed effects explain ~15% of the variation. I.e. Within individuals, just shy of half the variation in PPV is explained by change in ventilator settings.

```{r}
bayes_R2(m2)
```

```{r}
bayes_R2(m2, re_formula = NA)
```

# Make figure for m1 - No interaction

The following is the code to produce figure 5 in the paper.

## Plot observed PPV

Plot of observed PPV for all ventilator settings and both methods (GAM and Classic)

```{r out.width="80%"}
observed_plot <- ggplot(PPV_df_long, aes(label, PPV)) + 
  ggbeeswarm::geom_quasirandom(aes(color = PPV_method), 
                               dodge.width=.6,
                               width = 0.1,
                               size = 0.7,
                               shape=16) +
  guides(color = guide_legend(override.aes = list(alpha = 1, size = 1))) +
  scale_color_discrete(limits = c("gam", "classic"), labels = c("GAM", "Classic")) +
  labs(title = "Observed data", x="", y="PPV [%]",
       color = "PPV method",
       tag = "a") +
  theme(axis.text.x = element_text(hjust = 1, angle = 20),
        legend.position = c(0.5, 1),
        legend.direction = "horizontal",
        legend.justification = c(0.5,0.5),
        legend.box.background = element_rect(color = NA, fill = "white"),
        legend.text = element_text(size = rel(1)))

observed_plot
```

## Plot ventilation effects

```{r out.width="50%", fig.width=3, fig.height=3}
# Intercepts 
intercept_draws_m1 <- gather_draws(m1, `b_PPV_method(gam|classic)`, regex = TRUE) |> 
  mutate(PPV_method = str_remove(.variable, "b_PPV_method") |> 
           factor(levels = c("gam", "classic")),
         intercept = exp(.value),
         label = "VT=10, RR=10")

intercept_plot_m1 <- ggplot(intercept_draws_m1, aes(label, intercept, color = PPV_method)) +
  stat_pointinterval(point_size = 1, 
                     interval_size = 1,
                     position = position_dodge(width = 0.4),
                     .width = 0.95) +
  coord_cartesian(ylim = c(0, 20)) +
  labs(x="", y="PPV", tag = "b",
       title = "Intercepts") +
  theme(legend.position = "none")

intercept_plot_m1
```

```{r out.width="80%", fig.width=5}
# Contrasts
contrast_draws_m1 <- gather_draws(m1, `b_PPV_method(gam|classic):.+`, regex = TRUE) |> 
  separate(.variable, into = c("PPV_method", "setting"), sep = ":") |> 
  separate(setting, into = c("setting_type", "setting"), sep = "_f") |> 
  mutate(PPV_method = str_remove(PPV_method, "b_PPV_method") |> 
           factor(levels = c("gam", "classic")),
         rel_effect = exp(.value))

contrast_draws_vt_m1 <- filter(contrast_draws_m1, setting_type == "vent_rel_vt") |> 
  mutate(label = vt_levels[setting] |> factor(levels = vt_levels))

contrast_plot_layers <- list(
  stat_pointinterval(point_size = 1, 
                     interval_size = 1,
                     position = position_dodge(width = 0.4),
                     .width = 0.95),
  labs(y = "Relative effect", x = ""), 
  scale_y_continuous(labels = scales::label_percent(accuracy = 1),
                     breaks = seq(0.4, 1, by = 0.2)),
  coord_cartesian(ylim = c(0.4, 1)),
  theme(legend.position = "none")
)

contrast_plot_vt_m1 <- ggplot(contrast_draws_vt_m1, 
                              aes(label, rel_effect, color = PPV_method)) + 
  contrast_plot_layers +
  labs(title = "Effect of tidal volume (VT) on PPV", 
       subtitle = "Relative to VT=10 ml kg⁻¹", tag = "c")
  
  
contrast_draws_rr_m1 <- filter(contrast_draws_m1, setting_type == "vent_RR") |> 
  mutate(label = rr_levels[setting] |> factor(levels = rr_levels))

contrast_plot_rr_m1 <- ggplot(contrast_draws_rr_m1, 
                              aes(label, rel_effect, color = PPV_method)) +
  contrast_plot_layers +
  labs(title = "Effect of respiratory rate (RR) on PPV", 
       subtitle = "Relative to RR=10 min⁻¹", tag = "d")


contrast_plot_vt_m1 + contrast_plot_rr_m1
```

## Make figure 5 (without CV and residuals)

```{r}
param_plot_design_m1_simple <- "
  AAA
  BCD
"

m1_plot_simple <- observed_plot + 
  intercept_plot_m1 + contrast_plot_vt_m1 + contrast_plot_rr_m1 + 
  plot_layout(design = param_plot_design_m1_simple, 
              heights = c(2, 3),
              widths = c(1, 3, 3)
              ) 

save_plot("fig5_mix_model_fig", m1_plot_simple, width = 18, height = 11, scale = 1)

```

## Plot residuals

```{r out.width="80%", fig.width=5}
# Get mean residuals for both m1 and m2.
PPV_df_long_resid <- PPV_df_long |> 
  mutate(
    resid_m1 = residuals(m1, method = "posterior_predict")[,"Estimate"],
    resid_m2 = residuals(m2, method = "posterior_predict")[,"Estimate"]
  )

resid_plot_m1 <-  ggplot(PPV_df_long_resid, 
                         aes(label, resid_m1, color = PPV_method)) + 
  ggbeeswarm::geom_quasirandom(dodge.width=.6,
                               width = 0.1,
                               size = 0.5,
                               shape=16) +
  stat_summary(aes(color = NULL, group = PPV_method), fun = mean, geom = "point",
               shape = "-", size = 5, 
               position = position_dodge(width = 0.6)) +
  labs(title = "Model residuals (observed PPV - expected PPV)", 
       subtitle = "The horizontal segments are the means of the residuals",
       x="", y="Residual",
       tag = "e") +
  theme(axis.text.x = element_text(hjust = 1, angle = 20),
        legend.position = "none")

resid_plot_m1
```

## Plot residual standard deviation

Since we use a student t distribution for the likelihood, the sigma parameter does not equal the standard deviation (SD). SD of a T distribution is 

$$
SD = \sqrt{\sigma^2 \frac{\nu}{\nu-2}}, for\ \nu > 2 
$$

where $\nu$ (nu) is the degrees of freedom parameter.

```{r}
sd_t <- function(sigma, nu) {
  stopifnot(nu > 2)
  sqrt( sigma^2 * (nu / (nu-2)) )
}
```

```{r out.width="80%", fig.width=5}

# Make a data frame with one row for each combination of PPV_method and vent_setting
newdata_method_setting <- PPV_df_long |> 
  tidyr::expand(PPV_method, nesting(vent_setting, 
                                    vent_rel_vt, vent_RR,
                                    vent_rel_vt_f, vent_RR_f))

# Make draws of mean of posterior predictions (epred) 
# include sigma and nu for each draw (they are used to calculate SD).
vent_setting_epred_m1 <- newdata_method_setting |> 
  add_epred_draws(m1, re_formula = NA,
                  dpar = c("sigma", "nu")) |> 
  mutate(label = vent_setting_levels[as.character(vent_setting)] |> 
           factor(levels = vent_setting_levels),
         SD = sd_t(sigma, nu),
         CV = SD/.epred)

sd_plot_m1 <- ggplot(vent_setting_epred_m1, aes(label, 
                                              CV,
                                              color = PPV_method)) +
  stat_pointinterval(position = position_dodge(width = 0.3), 
                     .width = 0.95, interval_size = 1, 
                     point_size = 1, show.legend = FALSE) + 
  scale_y_continuous(limits = c(0, NA), labels = scales::label_percent()) + 
  labs(title = "Residual coefficient of variation [CV = SD(residuals) / E(PPV)]",
       x="", y="CV", color = "PPV method",
       tag = "f") +
  theme(axis.text.x = element_text(hjust = 1, angle = 20))

sd_plot_m1
```

## Combine plots in one figure

```{r}
param_plot_design_m1 <- "
  AAA
  BCD
  EEE
  FFF
"

m1_plot <- observed_plot + 
  intercept_plot_m1 + contrast_plot_vt_m1 + contrast_plot_rr_m1 + 
  resid_plot_m1 +
  sd_plot_m1 + 
  plot_layout(design = param_plot_design_m1, 
              heights = c(1, 1.5, 1, 1),
              widths = c(1, 3, 3)
              ) 

save_plot("suppl_m1_plot", m1_plot, width = 18, height = 18, scale = 1)
```

# Make table of relative effects for m1 (relative to VT=10 ml kg^-1^, RR=10 min^-1^)

These are the estimates that are visualized in panel c and d.

```{r}
contrast_draws_m1 |> 
  group_by(PPV_method, setting_type, setting) |>
  median_qi(rel_effect) |> 
  mutate(label = sprintf("%.0f [%.0f; %.0f]%%", 
                         rel_effect * 100, 
                         .lower * 100, 
                         .upper * 100)) |> 
  select(-c(.width, .point, .interval)) |> 
  knitr::kable(booktabs = TRUE, digits = 2)
```

# Compare m1 coefficient of variation (CV) between PPV~Classic~ and PPV~GAM~ across ventilator settings


```{r}
vent_setting_epred_m1 |> 
  ungroup() |> 
  pivot_wider(id_cols =c(.draw, vent_setting), 
              names_from = PPV_method, values_from = CV, names_prefix = "CV_") |> 
  mutate(CV_classic_m_gam = CV_classic - CV_gam) |> 
  group_by(vent_setting) |> 
  select(vent_setting, CV_classic_m_gam) |> 
  median_qi(CV_classic_m_gam) |> 
  mutate(label = sprintf("%.0f [%.0f; %.0f]%%-points", 
                         CV_classic_m_gam * 100, 
                         .lower * 100, 
                         .upper * 100)) |> 
  select(-c(.width, .point, .interval)) |> 
  knitr::kable(booktabs = TRUE, digits = 2)
```


# Make figure for m2 - Model that allows interaction of VT and RR effects

## Plot ventilation effects

```{r out.width="50%", fig.width=3, fig.height=3}
intercept_draws_m2 <- gather_draws(m2, `b_PPV_method(gam|classic)`, regex = TRUE) |> 
  mutate(PPV_method = str_remove(.variable, "b_PPV_method") |> 
           factor(levels = c("gam", "classic")),
         intercept = exp(.value),
         label = "VT=10, RR=10")

intercept_plot_m2 <- intercept_plot_m1 %+% intercept_draws_m2

intercept_plot_m2
```

```{r out.width="80%", fig.width=5}
contrast_draws_m2 <- gather_draws(m2, `b_PPV_method(gam|classic):.+`, regex = TRUE) |> 
  separate(.variable, into = c("PPV_method", "vent_setting"), sep = ":") |> 
  mutate(PPV_method = str_remove(PPV_method, "b_PPV_method") |> 
           factor(levels = c("gam", "classic")),
         vent_setting = str_remove(vent_setting, "vent_setting"),
         label = vent_setting_levels[vent_setting] |> 
           factor(levels = vent_setting_levels),
         rel_effect = exp(.value))

contrast_plot_m2 <- ggplot(contrast_draws_m2, 
                           aes(label, rel_effect, color = PPV_method)) + 
  stat_pointinterval(point_size = 1, 
                     interval_size = 1,
                     position = position_dodge(width = 0.4),
                     .width = 0.95) +
  labs(y = "Relative effect", x = "",
       title = "Effect of tidal volume (VT) and respiratory rate (RR) on PPV", 
       subtitle = "Relative to VT=10 ml kg⁻¹ and RR = 10 min⁻¹", tag = "c") + 
  scale_y_continuous(labels = scales::label_percent(accuracy = 1),
                     breaks = seq(0.4, 1, by = 0.2)) +
  coord_cartesian(ylim = c(0.3, 1)) +
  theme(legend.position = "none",
        axis.text.x = element_text(hjust = 1, angle = 20)) 
  
  
contrast_plot_m2
```

## Plot residuals

```{r out.width="80%", fig.width=5}
resid_plot_m2 <-  ggplot(PPV_df_long_resid, aes(label, resid_m2)) + 
  ggbeeswarm::geom_quasirandom(aes(color = PPV_method), 
                               dodge.width=.6,
                               width = 0.1,
                               size = 0.7,
                               shape=16) +
  stat_summary(aes(color = NULL, group = PPV_method), fun = mean, geom = "point",
               shape = "-", size = 5, 
               position = position_dodge(width = 0.6)) +
  labs(title = "Model residuals (observed PPV - expected PPV)", 
       subtitle = "The horizontal segments are the means of the residuals",
       x="", y="Residual",
       tag = "d") +
  theme(axis.text.x = element_text(hjust = 1, angle = 20),
        legend.position = "none")

resid_plot_m2
```

## Plot residual standard deviation

```{r out.width="80%", fig.width=5}
# Make draws of mean of posterior predictions (epred) 
# include sigma for each draw.

vent_setting_epred_m2 <- newdata_method_setting |> 
  add_epred_draws(m2, re_formula = NA,
                  dpar = c("sigma", "nu")) |> 
  mutate(label = vent_setting_levels[as.character(vent_setting)] |> 
           factor(levels = vent_setting_levels),
         SD = sd_t(sigma, nu),
         CV = SD/.epred)

# Reuse the sd plot from model 1, but with new data
sd_plot_m2 <- sd_plot_m1 %+% vent_setting_epred_m2 +
  labs(tag = "e")

sd_plot_m2
```

## Combine plots in one figure
```{r, fig.width=7, fig.height=10, out.width="100%"}
param_plot_design_m2 <- "
  AA
  BC
  DD
  EE
"

m2_plot <- observed_plot + 
  intercept_plot_m2 + 
  contrast_plot_m2 + 
  resid_plot_m2 +
  sd_plot_m2 + 
  plot_layout(design = param_plot_design_m2, 
              heights = c(1, 1.5, 1, 1),
              widths = c(1, 5)
              ) 

save_plot("extra_m2_plot", m2_plot, width = 18, height = 18, scale = 1)

m2_plot
```

