---
title: "Supplementary figures and tables"
output:
  bookdown::pdf_document2:
    extra_dependencies: ["underscore", "float"]
    toc: no
    dev: cairo_pdf
    latex_engine: xelatex
    number_sections: no
# toc-title: "Contents"
fontsize: 11pt
geometry: margin=2cm
linkcolor: NavyBlue
monofont: FreeMono
monofontoptions: 'Scale=0.8'
mainfontoptions: 'Linestretch=4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{=tex}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\thefigure}{S\arabic{figure}}
```

# Figure S1

```{r}
#| fig.cap = "Scatter plots of the relation between PPV calculated with the classic algorithm (PPV~Classic~) and the stroke volume response (ΔSV) to a 250 ml fluid challenge. Panels are arranged with tidal volumes (VT) in rows and respiratory rates (RR) in columns . One fluid challenge was evaluated for each subject (n = 50), while PPV~Classic~ was calculated for each of the 10 ventilator settings."
knitr::include_graphics("plots/suppl_fluid_prediction_classic.pdf")
```

\newpage

# Figure S2

(ref:fig2) Receiver operating characteristic (ROC) curves for capacity of pulse pressure variation (PPV) to classify fluid responsiveness (stroke volume change > 10%). Panels are arranged with tidal volumes (VT) in rows and respiratory rates (RR) in columns. One fluid challenge was evaluated for each subject (n = 50), while PPV~GAM~ and PPV~Classic~ was calculated for each of the 10 ventilator settings.

```{r, out.width = "95%"}
#| fig.cap = "(ref:fig2)"
knitr::include_graphics("plots/suppl_ROC_curves.pdf")
```

\newpage

# Figure S3

```{r}
#| fig.cap = "Bland-Altman plots showing the relation between PPV~GAM~ and PPV~Classic~. The outer dashed lines represent 95% limits of agreement (LoA). Grey areas are 95% confidence intervals for bias and LoA. The purple lines and areas are linear regression fits with 95% confidence intervals. Panels are arranged with tidal volumes (VT) in rows and respiratory rates (RR) in columns."
knitr::include_graphics("plots/suppl_PPV_BA_gam_vs_classic.pdf")
```

\newpage

# Figure S4

(ref:fig4) (Extended version of the paper's Fig. 5): Parameter estimates for a Bayesian mixed-effects model, describing the effect of tidal volume (VT) and respiratory rate (RR) on pulse pressure variation (PPV). Parameters are estimated for both PPV derived using a generalized additive model (GAM) and using a classic approach (Classic). Panel **a** presents the observed PPV values (outcomes) using each method (n=507 for both GAM and Classic). Vertical bars are 95% compatibility intervals. Panel **b**, **c** and **d** present parameter estimates. Vertical bars are 95% compatibility intervals. Panel **e** shows model residuals, and panel **f** shows the residual variation relative to the estimated value of PPV.

```{r, out.width="85%", fig.align='center'}
#| fig.cap = "(ref:fig4)"
knitr::include_graphics("plots/suppl_m1_plot.pdf")
```

\newpage

# Table S1

```{r, out.width="90%"}
knitr::include_graphics("tables/roc_table.pdf")
```


